Clustering: A pipeline to analyse time-course gene expression data

### 2019-02-17 scripts/03_clustering.Rmd
ENH filtering on lfc
ENH switching to viridis for better colors

```{r}
if(filter_genes){
    # First, filter out any genes that doesn't have a log fold change of at
    # least 2
    # XXX I should actually filter on the max, but it is broken right now.
    lfc_col_to_keep = colnames(pvalues)[
	grepl("-lfc_epicon", colnames(pvalues))]
    pvalues = pvalues[rowSums(abs(pvalues[, lfc_col_to_keep]) > 2) > 0, ]

@@

@@

```{r}
moanin::plot_centroids(centroids, meta)
```

```{r results="hide", echo=FALSE}
# Save the clustering for the next step
write.table(labels, ".results/clustering_labels.txt", sep="\t")
```

>>>>

```{r}
if(filter_genes){
    # First, filter out any genes that doesn't have a log fold change of at
    # least 2
    # XXX I should actually filter on the max, but it is broken right now.
    lfc_col_to_keep = colnames(pvalues)[
	grepl("-lfc_max", colnames(pvalues))]
    pvalues = pvalues[rowSums(abs(pvalues[, lfc_col_to_keep]) > 2) > 0, ]

@@

```{r}
table(kmeans_clusters$clusters)
```

@@

```{r fig.height=8, fig.width=8}
moanin::plot_centroids(centroids, meta)
```

```{r results="hide", echo=FALSE}
# Save the clustering for the next step
write.table(kmeans_clusters$clusters,
	    ".results/clustering_labels.txt",
	    sep="\t")
```
